Covariate analysis of MSSM reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-04-25 code/Rmd/MSSM_REPROCESSED.Rmd
Minor bug fix

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION$E.zero, 
                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

@@

tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`
### Sanity check
```{r residual.adj, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION$expr.zero, 
                                              COVARIATES,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)

>>>>

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  tmp.expr = RESIDUAL.GENE_EXPRESSION$expr.zero
  tmp.expr = tmp.expr[apply(tmp.expr, 1, var) != 0,]
  residualSigCovars = runPCAandPlotCorrelations(tmp.expr, 
                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

@@

tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`
### Sanity check
```{r residual.adj, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
tmp.expr = RESIDUAL.GENE_EXPRESSION$expr.zero
tmp.expr = tmp.expr[apply(tmp.expr, 1, var) != 0,]
residualSigCovars = runPCAandPlotCorrelations(tmp.expr, 
                                              COVARIATES,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
